\pkg{evtree}: Evolutionary Learning of Globally Optimal Classification and Regression Trees in \proglang{R}

### 2011-09-28 pkg/evtree/inst/doc/evtree.Rnw
some touch ups in notation
shortened/simplified crossover section further

two additional \pagebreak to prettify layout



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@251 255f4249-2263-4417-b1ea-8498779e27a7

\pagebreak

@@

Classification and regression tree analysis aims at
modeling a response variable $Y$ by a vector of $P$ predictor variables
$X=(X_1,...,X_P)$ where for classification trees $Y$ is
qualitative and for regression trees $Y$ is quantitative. Tree-based methods
first partition the input space $X$ into a set of $M$ rectangular regions $R_m$
($m = 1,...,M$) then fit a (typically simple) model within each region $\{Y | X \in R_m\}$,
e.g., the mean, median, or variance etc. Typically, the mode is used for
classification trees and the arithmetic mean is applied for regression trees.

@@

Instead of searching all combinations in $\Theta$ simultaneously, recursive
partitioning algorithms only consider one split at a time. At each internal node
$r \in \{n_1,..., n_{M-1}\}$, the split variable $v_r$ and the corresponding
split point $s_r$ are selected to locally minimize the loss function.
Starting with an empty tree $\theta_0 = (\emptyset)$, the tree is first grown 
recursively and subsequently \emph{pruned} to satisfy the complexity tradeoff:
%
\begin{eqnarray} \label{eq:locally}
  \bar \theta_r
    & = & \argmin_{ \theta = \theta_{r-1} \cup (v_r, s_r)} \; \mathrm{loss}\{Y, f(X, \theta)\} 
    \qquad (r = 1, \dots, M_{\max} -1), \\
  \bar \theta
    & = & \argmin_{\bar \theta_r} \; \mathrm{loss}\{Y, f(X, \bar \theta_r)\} ~+~ \mathrm{comp}(\bar \theta_r).
  \label{eq:pruning}
\end{eqnarray}
%
For nontrivial problems, forward-search recursive partitioning methods only search a small
fraction of the global search space $(v_1, s_1, \dots, v_{M_{\max}-1},
s_{M_{\max}-1} )$. They only search each $(v_r, s_r)$ once, and independently of
the subsequent split rules, hence typically leading to a globally suboptimal solution
$\bar \theta$.

@@

When compared with the described forward stepwise search, a less greedy approach
is to calculate the effects of the split rules deeper down in the
tree. In this way optimal trees can be found for simple problems. However,
split selection at a given node in Equation~\ref{eq:locally} has complexity  $O(PN)$
(if all $P$ variables are numeric/ordered with $N$ distinct values).
Through a global search up to $D-1$ levels (\ref{eq:globally}) the complexity
increases to $O(P^D N^D)$ \citep{papagelis2001bdt}. One conceivable compromise
between these two extremes is to look ahead $d$~steps with $1 < d < D$
\citep[see e.g.,][]{esmeir2007ald}, also yielding a locally optimal tree but
less constrained than that from a 1-step-ahead search.
Another class of algorithms is given by stochastic optimization methods that,
given an initial tree, seek improved solutions through stochastic changes to
the tree structure. Thus, these algorithms try to explore the full parameter
space $\Theta$ but cannot be guaranteed to find the globally optimal solution
but only an approximation thereof. Besides evolutionary algorithms
\citep{koza1991concept}, \textit{Bayesian CART} \citep{denison1998bca} and
\textit{simulated annealing} \citep{sutton1992ict} were used successfully to
solve difficult classification and regression tree problems.
\cite{koza1991concept} first formulated the concept of using evolutionary
algorithms as a stochastic optimization method to build classification and
regression trees. \cite{papagelis2001bdt} presented a classification tree
algorithm and provided results on several datasets from the UCI machine learning
repository \citep{Frank+Asuncion:2010}. Another method for the construction of
classification and regression trees via evolutionary algorithms was introduced by
\cite{gray2008cta} and \cite{fan2005rta}, respectively.
\cite{cantu2003inducing} used an evolutionary algorithm to induce so-called oblique
classification trees.

@@

Each tree of the population is initialized with a valid, randomly generated,
split rule in the root node. First, $v_1$ is selected with uniform probability
from $1,...,P$. Second, a split point $s_1$ is selected. If $X_{v_1}$ is numeric
or ordinal with $u$ unique values, a split point $s_1$ is selected with uniform
probability from the $u-1$ possible spit points of $X_{v_1}$. If $X_{v_1}$ is
nominal and has $c$ categories, each $k=1,...,c$ has a probability of $50\%$ to
be assigned to the left or the right daughter node. In cases where all $k$ are
allocated to the same terminal node, the assignment of one category is flipped
to the other terminal node. If this procedure results in a non-valid split rule,
the two steps of random split variable selection and split point selection are
repeated. With the definition of $r=1$ and the selection of $v_1$ and $s_1$, the
initialization is complete and each individual of the population of trees is of
type $\tilde{\theta}_{1}= (v_1, s_1)$.

@@

The search for a valid split rule is conducted as in see Section~\ref{init}
for a maximum of $P$ iterations. 
In cases where no valid split rule can be assigned to the internal node at
position $r$, the search for a valid split rule is carried out on another
randomly selected terminal node. If, after 10~attempts, no valid split rule
can be found, then $\tilde{\theta}_{i+1} = \tilde{\theta}_{i}$. Otherwise, the
set of parameters in iteration $i+1$ are given by $\tilde{\theta}_{i+1}=
\tilde{\theta}_i \cup (v_{r},s_{r})$.

@@

\textit{Prune} chooses a random internal node $r$, where $r>1$, which has two
terminal nodes as successors and prunes it into a terminal node. The tree's
parameters at iteration $i+1$ are $\tilde{\theta}_{i+1}=\tilde{\theta}_{i}
\setminus (v_{r},s_{r})$. If $\tilde{\theta}_{i}$ only comprises one internal
node, i.e., the root node, then $\tilde{\theta}_{i+1} = \tilde{\theta}_{i}$.

@@

If no pruning occurs, $\tilde{\theta}_{i}$ and $\tilde{\theta}_{i+1}$ contain
the same set of parameters. Otherwise, the set of parameters $(v_{m_1}, s_{m_1},
..., v_{m_f}, s_{m_f})$, corresponding to invalid nodes, is removed from
$\tilde{\theta}_i$. Thus, $\tilde{\theta}_{i+1} = \tilde{\theta}_{i} \setminus
(v_{m_1}, s_{m_1}, ..., v_{m_f}, s_{m_f})$.

@@

Equivalently to the \textit{major split rule mutation} operator the subsequent
solution $\tilde{\theta}_{i+1} = \tilde{\theta}_{i} \setminus (v_{m_1}, s_{m_1},
..., v_{m_f}, s_{m_f})$.

@@

\textit{Crossover} exchanges, randomly selected, subtrees between two trees. Let
$\tilde{\theta}_{i}^1$ and $\tilde{\theta}_{i}^2$ be the parameters of the trees
that are chosen for crossover. First, an internal node is selected randomly from
each of $\tilde{\theta}_{i}^1$ and $\tilde{\theta}_{i}^2$, which we denote as
$r_1$ and $r_2$. Let $\mathrm{sub}1(\tilde{\theta}_i^j, r_j)$ denote the subtrees
rooted by $r_j$ ($j=1,2$). Thus, $\mathrm{sub}1(\tilde{\theta}_i^j, r_j)$ contains $r_j$, 
and its descendant nodes. Then, the complementary part of $\tilde{\theta}_{i}^j$ can be 
defined as 
$\mathrm{sub}2(\tilde{\theta}_{i}^j, r_j) =  \tilde{\theta}_{i}^j \setminus \mathrm{sub}1(\tilde{\theta}_{i}^j, r_j)$.

After the application of the \textit{crossover} operator, the trees' parameter
spaces are given by $\tilde{\theta}_{i+1}^1= \mathrm{sub}2(\tilde{\theta}_{i}^1, r_1)
\cup \mathrm{sub}1(\tilde{\theta}_{i}^2, r_2) \setminus (v_{m_{21}}, s_{m_{21}}, ...,
v_{m_{2f}}, s_{m_{2f}})$ and $\tilde{\theta}_{i+1}^2=
\mathrm{sub}2(\tilde{\theta}_{i}^2, r_2) \cup \mathrm{sub}1(\tilde{\theta}_{i}^1, r_1)
\setminus (v_{m_{11}}, s_{m_{11}}, ..., v_{m_{1f}}, s_{m_{1f}})$. Here,
$(v_{m_{11}}, s_{m_{11}}, ..., v_{m_{1f}}, s_{m_{1f}}) \subset
\mathrm{sub}1(\tilde{\theta}_i^1, r_1)$ and   
$(v_{m_{21}}, s_{m_{21}}, ...,v_{m_{2f}}, s_{m_{2f}}) \subset \mathrm{sub}1(\tilde{\theta}_i^2, r_2)$ 
are the parameters of the invalid nodes.

@@

Our algorithm uses $(1+1)$ selection, where one parent solution
competes with one offspring for a place in the population. In the case of a
mutation operator either the solution before $\tilde{\theta}_i$ or after
modification $\tilde{\theta}_{i+1}$ is kept in memory. In the case of the
crossover operator, the initial solutions of $\tilde{\theta}_i^1$ competes with
its subsequent solutions $\tilde{\theta}_{i+1}^1$. Correspondingly, one of the
two solutions $\tilde{\theta}_i^2$ and $\tilde{\theta}_{i+1}^2$ is rejected. The
survivor selection is done deterministically. The tree with lower fitness,
according to the evaluation function, is rejected. Note that, due to the
definition of the crossover operator, some trees are selected more than
once in an iteration. Correspondingly, these trees undergo the survival
selection process more than once in an iteration.

@@

First, the data is loaded and the forward-search trees are grown
with and without depth restriction, visualizing the unrestricted trees
in Figure~\ref{fig:example_rpart_ctree}.
%
<<BBBClub-rpart-ctree, echo=TRUE, eval=FALSE>>=
data("BBBClub", package = "evtree")
library("rpart")
rp  <- as.party(rpart(choice ~ ., data = BBBClub, minbucket = 10))
rp2 <- as.party(rpart(choice ~ ., data = BBBClub, minbucket = 10,
  maxdepth = 2))
ct  <- ctree(choice ~ ., data = BBBClub, minbucket = 10, mincrit = 0.99)
ct2 <- ctree(choice ~ ., data = BBBClub, minbucket = 10, mincrit = 0.99,
  maxdepth = 2)
plot(rp)
plot(ct)
@
%
With the objective of building a smaller, but at still accurate tree,
\code{evtree} is constrained to a maximum tree depth of $2$,
see Figure~\ref{fig:example_evtree}.
%
<<BBBClub-evtree, echo=TRUE, eval=FALSE>>=
set.seed(1090)
ev <- evtree(choice ~ ., data = BBBClub, minbucket = 10, maxdepth = 2)
@
%
<<BBBClub-cache, echo=FALSE, eval=TRUE>>=
if(cache & file.exists("BBBClub-trees.rda")) {
load("BBBClub-trees.rda")
} else {
<<BBBClub-rpart-ctree>>
<<BBBClub-evtree>>
if(cache) {
  save(rp, rp2, ct, ct2, ev, file = "BBBClub-trees.rda")
} else {
  if(file.exists("BBBClub-trees.rda")) file.remove("BBBClub-trees.rda")
}
}
@
%
\setkeys{Gin}{width=1\textwidth}
\begin{figure}[p!]
\centering
\begin{minipage}{1\textwidth}
\begin{flushleft} \code{rpart} \end{flushleft}
\centering
\setkeys{Gin}{width=0.75\textwidth}
<<BBBClub-rpart-plot, fig=TRUE, echo=FALSE, width=8.1, height=7>>=
plot(rp)
@
\end{minipage}
\begin{minipage}{1\textwidth}
\begin{flushleft} \code{ctree} \end{flushleft}
\centering
\setkeys{Gin}{width=1\textwidth}
<<BBBClub-ctree-plot, fig=TRUE, echo=FALSE,  width=11.4, height=5.9>>=
plot(ct)
@
\end{minipage}
\caption{\label{fig:example_rpart_ctree} Trees for customer targeting constructed by \code{rpart}
  (upper panel) and \code{ctree} (lower panel). The target variable is the customer's choice of buying the book.
  The variables used for splitting are the number of art books purchased previously (\code{art}), the number
  of months since the first purchase (\code{first}), the frequency of previous purchases at the Bookbinder's Book Club
  (\code{freq}) and the customer's \code{gender}.}
\end{figure}
%
The resulting evolutionary tree is printed below and visualized in
Figure~\ref{fig:example_evtree}.
%
<<BBBClub-evtree-display>>=
plot(ev)
ev
@
%
\setkeys{Gin}{width=1\textwidth}
\begin{figure}[t!]
\begin{flushleft} \code{evtree} \end{flushleft}
\centering
\setkeys{Gin}{width=0.7\textwidth}
<<BBBClub-evtree-plot, fig=TRUE, echo=FALSE, width=7.5, height=4.9>>=
plot(ev)
@
\caption{\label{fig:example_evtree} Tree for customer targeting constructed by \code{evtree}
   The target variable is the customer's choice of buying the book. The variables used for splitting are
   the number of art books purchased previously (\code{art}) and the number of months since the first purchase
    \code{first}.}
\end{figure}

@@

>>>>

\pagebreak %%FIXME

@@

Classification and regression tree analysis aims at
modeling a response variable $Y$ by a vector of $P$~predictor variables
$X=(X_1,...,X_P)$ where for classification trees $Y$ is
qualitative and for regression trees $Y$ is quantitative. Tree-based methods
first partition the input space $X$ into a set of $M$ rectangular regions $R_m$
($m = 1,...,M$) then fit a (typically simple) model within each region $\{Y | X \in R_m\}$,
e.g., the mean, median, or variance etc. Typically, the mode is used for
classification trees and the arithmetic mean is applied for regression trees.

@@

Instead of searching all combinations in $\Theta$ simultaneously, recursive
partitioning algorithms only consider one split at a time. At each internal node
$r \in \{n_1,..., n_{M-1}\}$, the split variable $v_r$ and the corresponding
split point $s_r$ are selected to locally minimize the loss function.
Starting with an empty tree $\theta_0 = (\emptyset)$, the tree is first grown 
recursively and subsequently \emph{pruned} to satisfy the complexity tradeoff:
%
\begin{eqnarray} \label{eq:locally}
  \tilde \theta_r
    & = & \argmin_{ \theta = \theta_{r-1} \cup (v_r, s_r)} \; \mathrm{loss}\{Y, f(X, \theta)\} 
    \qquad (r = 1, \dots, M_{\max} -1), \\
  \tilde \theta
    & = & \argmin_{\tilde \theta_r} \; \mathrm{loss}\{Y, f(X, \tilde \theta_r)\} ~+~ \mathrm{comp}(\tilde \theta_r).
  \label{eq:pruning}
\end{eqnarray}
%
For nontrivial problems, forward-search recursive partitioning methods only search a small
fraction of the global search space $(v_1, s_1, \dots, v_{M_{\max}-1},
s_{M_{\max}-1} )$. They only search each $(v_r, s_r)$ once, and independently of
the subsequent split rules, hence typically leading to a globally suboptimal solution
$\tilde \theta$.

@@

When compared with the described forward stepwise search, a less greedy approach
is to calculate the effects of the split rules deeper down in the
tree. In this way optimal trees can be found for simple problems. However,
split selection at a given node in Equation~\ref{eq:locally} has complexity  $O(PN)$
(if all $P$~variables are numeric/ordered with $N$ distinct values).
Through a global search up to $D-1$ levels (\ref{eq:globally}) the complexity
increases to $O(P^D N^D)$ \citep{papagelis2001bdt}. One conceivable compromise
between these two extremes is to look ahead $d$~steps with $1 < d < D$
\citep[see e.g.,][]{esmeir2007ald}, also yielding a locally optimal tree but
less constrained than that from a 1-step-ahead search.
Another class of algorithms is given by stochastic optimization methods that,
given an initial tree, seek improved solutions through stochastic changes to
the tree structure. Thus, these algorithms try to explore the full parameter
space $\Theta$ but cannot be guaranteed to find the globally optimal solution
but only an approximation thereof. Besides evolutionary algorithms
\citep{koza1991concept}, \textit{Bayesian CART} \citep{denison1998bca} and
\textit{simulated annealing} \citep{sutton1992ict} were used successfully to
solve difficult classification and regression tree problems.
\cite{koza1991concept} first formulated the concept of using evolutionary
algorithms as a stochastic optimization method to build classification and
regression trees. \cite{papagelis2001bdt} presented a classification tree
algorithm and provided results on several datasets from the UCI machine learning
repository \citep{Frank+Asuncion:2010}. Another method for the construction of
classification and regression trees via evolutionary algorithms was introduced by
\cite{gray2008cta} and \cite{fan2005rta}, respectively.
\cite{cantu2003inducing} used an evolutionary algorithm to induce so-called oblique
classification trees.

@@

Each tree of the population is initialized with a valid, randomly generated,
split rule in the root node. First, $v_1$ is selected with uniform probability
from $1,...,P$. Second, a split point $s_1$ is selected. If $X_{v_1}$ is numeric
or ordinal with $u$ unique values, a split point $s_1$ is selected with uniform
probability from the $u-1$ possible spit points of $X_{v_1}$. If $X_{v_1}$ is
nominal and has $c$ categories, each $k=1,...,c$ has a probability of $50\%$ to
be assigned to the left or the right daughter node. In cases where all $k$ are
allocated to the same terminal node, the assignment of one category is flipped
to the other terminal node. If this procedure results in a non-valid split rule,
the two steps of random split variable selection and split point selection are
repeated. With the definition of $r=1$ and the selection of $v_1$ and $s_1$, the
initialization is complete and each individual of the population of trees is of
type ${\theta}_{1}= (v_1, s_1)$.

@@

The search for a valid split rule is conducted as in see Section~\ref{init}
for a maximum of $P$~iterations. 
In cases where no valid split rule can be assigned to the internal node at
position~$r$, the search for a valid split rule is carried out on another
randomly selected terminal node. If, after 10~attempts, no valid split rule
can be found, then ${\theta}_{i+1} = {\theta}_{i}$. Otherwise, the
set of parameters in iteration $i+1$ are given by ${\theta}_{i+1}=
{\theta}_i \cup (v_{r},s_{r})$.

@@

\textit{Prune} chooses a random internal node $r$, where $r>1$, which has two
terminal nodes as successors and prunes it into a terminal node. The tree's
parameters at iteration $i+1$ are ${\theta}_{i+1}={\theta}_{i}
\setminus (v_{r},s_{r})$. If ${\theta}_{i}$ only comprises one internal
node, i.e., the root node, then ${\theta}_{i+1} = {\theta}_{i}$.

@@

If no pruning occurs, ${\theta}_{i}$ and ${\theta}_{i+1}$ contain
the same set of parameters. Otherwise, the set of parameters $(v_{m_1}, s_{m_1},
..., v_{m_f}, s_{m_f})$, corresponding to invalid nodes, is removed from
${\theta}_i$. Thus, ${\theta}_{i+1} = {\theta}_{i} \setminus
(v_{m_1}, s_{m_1}, ..., v_{m_f}, s_{m_f})$.

@@

Equivalently to the \textit{major split rule mutation} operator the subsequent
solution ${\theta}_{i+1} = {\theta}_{i} \setminus (v_{m_1}, s_{m_1},
..., v_{m_f}, s_{m_f})$.

@@

\textit{Crossover} exchanges, randomly selected, subtrees between two trees. Let
${\theta}_{i}^1$ and ${\theta}_{i}^2$ be the two trees
chosen from the population for crossover. First, an internal nodes $r_1$ and $r_2$
are selected randomly from ${\theta}_{i}^1$ and ${\theta}_{i}^2$, respectively.
Let $\mathrm{sub}1({\theta}_i^j, r_j)$ denote the subtree of $\theta_j$ rooted
by $r_j$ ($j=1,2$), i.e., the tree containing $r_j$ and its descendant nodes.
Then, the complementary part of ${\theta}_{i}^j$ can be defined as 
$\mathrm{sub}2({\theta}_{i}^j, r_j) = {\theta}_{i}^j \setminus \mathrm{sub}1({\theta}_{i}^j, r_j)$. 
The crossover operator creates two new trees
${\theta}_{i+1}^1 = \mathrm{sub}2({\theta}_{i}^1, r_1) \cup \mathrm{sub}1({\theta}_{i}^2, r_2)$ and
${\theta}_{i+1}^2 = \mathrm{sub}2({\theta}_{i}^2, r_2) \cup \mathrm{sub}1({\theta}_{i}^1, r_1)$.
If the crossover creates some invalid nods in either one of the new trees ${\theta}_{i+1}^1$
or ${\theta}_{i+1}^2$, these are omitted.

@@

Our algorithm uses $(1+1)$ selection, where one parent solution
competes with one offspring for a place in the population. In the case of a
mutation operator either the solution before ${\theta}_i$ or after
modification ${\theta}_{i+1}$ is kept in memory. In the case of the
crossover operator, the initial solutions of ${\theta}_i^1$ competes with
its subsequent solutions ${\theta}_{i+1}^1$. Correspondingly, one of the
two solutions ${\theta}_i^2$ and ${\theta}_{i+1}^2$ is rejected. The
survivor selection is done deterministically. The tree with lower fitness,
according to the evaluation function, is rejected. Note that, due to the
definition of the crossover operator, some trees are selected more than
once in an iteration. Correspondingly, these trees undergo the survival
selection process more than once in an iteration.

@@

First, the data is loaded and the forward-search trees are grown
with and without depth restriction, visualizing the unrestricted trees
in Figure~\ref{fig:example_rpart_ctree}.
%
<<BBBClub-rpart-ctree, echo=TRUE, eval=FALSE>>=
data("BBBClub", package = "evtree")
library("rpart")
rp  <- as.party(rpart(choice ~ ., data = BBBClub, minbucket = 10))
rp2 <- as.party(rpart(choice ~ ., data = BBBClub, minbucket = 10,
  maxdepth = 2))
ct  <- ctree(choice ~ ., data = BBBClub, minbucket = 10, mincrit = 0.99)
ct2 <- ctree(choice ~ ., data = BBBClub, minbucket = 10, mincrit = 0.99,
  maxdepth = 2)
plot(rp)
plot(ct)
@
%
With the objective of building a smaller, but at still accurate tree,
\code{evtree} is constrained to a maximum tree depth of $2$,
see Figure~\ref{fig:example_evtree}.
%
<<BBBClub-evtree, echo=TRUE, eval=FALSE>>=
set.seed(1090)
ev <- evtree(choice ~ ., data = BBBClub, minbucket = 10, maxdepth = 2)
@
%
<<BBBClub-cache, echo=FALSE, eval=TRUE>>=
if(cache & file.exists("BBBClub-trees.rda")) {
load("BBBClub-trees.rda")
} else {
<<BBBClub-rpart-ctree>>
<<BBBClub-evtree>>
if(cache) {
  save(rp, rp2, ct, ct2, ev, file = "BBBClub-trees.rda")
} else {
  if(file.exists("BBBClub-trees.rda")) file.remove("BBBClub-trees.rda")
}
}
@
%
\setkeys{Gin}{width=1\textwidth}
\begin{figure}[p!]
\centering
\begin{minipage}{1\textwidth}
\begin{flushleft} \code{rpart} \end{flushleft}
\centering
\setkeys{Gin}{width=0.75\textwidth}
<<BBBClub-rpart-plot, fig=TRUE, echo=FALSE, width=8.1, height=7>>=
plot(rp)
@
\end{minipage}
\begin{minipage}{1\textwidth}
\begin{flushleft} \code{ctree} \end{flushleft}
\centering
\setkeys{Gin}{width=1\textwidth}
<<BBBClub-ctree-plot, fig=TRUE, echo=FALSE,  width=11.4, height=5.9>>=
plot(ct)
@
\end{minipage}
\caption{\label{fig:example_rpart_ctree} Trees for customer targeting constructed by \code{rpart}
  (upper panel) and \code{ctree} (lower panel). The target variable is the customer's choice of buying the book.
  The variables used for splitting are the number of art books purchased previously (\code{art}), the number
  of months since the first purchase (\code{first}), the frequency of previous purchases at the Bookbinder's Book Club
  (\code{freq}) and the customer's \code{gender}.}
\end{figure}
%
The resulting evolutionary tree is printed below and visualized in
Figure~\ref{fig:example_evtree}.
%
<<BBBClub-evtree-display>>=
plot(ev)
ev
@
%
\setkeys{Gin}{width=1\textwidth}
\begin{figure}[t!]
\begin{flushleft} \code{evtree} \end{flushleft}
\centering
\setkeys{Gin}{width=0.75\textwidth} %FIXME: 0.75 just to avoid \pagebreak, should be 0.7
<<BBBClub-evtree-plot, fig=TRUE, echo=FALSE, width=7.5, height=4.9>>=
plot(ev)
@
\caption{\label{fig:example_evtree} Tree for customer targeting constructed by \code{evtree}
   The target variable is the customer's choice of buying the book. The variables used for splitting are
   the number of art books purchased previously (\code{art}) and the number of months since the first purchase
    \code{first}.}
\end{figure}

@@

\pagebreak %%FIXME
